What can GitHub and Googlecode Issues tell us about Exceptions in Android and Java?

### 2014-09-01 android-stacks.tex
including last data from manual inspections of CG collected by Lucas

@@

Runtime	&	1075 	&	56	&	1446	&	374	&	2951 / 956\\
Error	&	144	&	34	&	168	&	105	&		451 /  250	\\
Checked	&	110	&	230	&	139	&	145	&	624  /  734	\\
Throwable	&	0	&	0	&	1	&	0	&	1 / 1	\\
Undefined	&	1	&	0	&	6	&	8	&	15 / 46	\\ %22 DISTINCT EXCEPTIONS AND 9 IN GIT
    \hline
All		& 1330	&	320	&	1760	&	632	&	4042	\\
    \hline
  \end{tabular}
\caption{Types of root exceptions.}
  \label{tab:typeroottab}
\end{table}

@@

\begin{table*}
  \centering
  \begin{tabular}{llcccccc}
    \hline
    \bfseries{Wrapper Type}  &  \bfseries{Root Cause Type} &  \bfseries{Projects}  &  \bfseries{Occurrences} & \textsf{Android} & \textsf{Java/Libcore} & \textsf{Lib} & \textsf{App}  \\
    \hline
      Runtime &  Checked   & 70 & 114 & 66 &  0  & 19 &  29 \\
      Runtime   &  Error   & 38  & 57 & 50 &  0  & 6 &  1 \\
      Checked &  Runtime   & 12 & 22 & 4 &  0  & 9 &  9 \\
      Checked & Error      & 7 &  8 & 5 &  0  & 0 &  3 \\
      Error & Checked      & 4  &  7 & 0 &  7  & 0 &  0     \\
      Error & Runtime     & 6  &  13   & 1 &  1  & 0 &  11    \\
    \hline
      %none   & Runtime   &  2360 & 359 \\
      %none  &   Checked  & 422  & 117 \\
      %none  &   Error   & 381  & 141 \\
      %none &  Undefined  &  15   & 10  \\
      %none & Throwable  &  1    & 1 \\
     %\hline
      %Runtime   & Runtime & 560  & 182 \\    
      %Checked   & Checked & 98   & 42  \\
      %Error     & Error   & 15   & 14  \\
    %\hline
  \end{tabular}
\caption{Wrappings comprising different exception types.}
\label{tab:wrappingandroid}
\end{table*}

>>>>

%SELECT COUNT(*) FROM STACKTRACESUMMARY WHERE
%repo !='android'  AND MAIN_EXTENDS LIKE 'RUNT%' AND MAINSIGNALER_FROM like 'APP%';

@@

Runtime	&	1075 / 160	&	56 	&	1446 / 397	&	374	/  386  &	2951 / 943\\
Error	       &	 144	 / 32              &	34	&	168	 / 134               &	105	 / 74           &	451 /  240	\\
Checked	&	110	   / 39           &	230	&	139	  / 174            &	145	 / 466           &	624  /  679	\\
Throwable	&	0 /0	       &	0	&	1 / 1	             &	0	     / 0               &	1 / 1	\\
Undefined	&	1 / 1 	&	0	&	6 / 	12		&	8	/ 32	   &	15 / 45	\\ %22 DISTINCT EXCEPTIONS AND 9 IN GIT
    \hline
All		& 1330	&	320	&	1760	&	632	&	4042	\\
    \hline
  \end{tabular}
\caption{Types of root exceptions.}
  \label{tab:typeroottab}
\end{table}

@@

%SELECT COUNT(*) FROM STACKTRACESUMMARY WHERE
%repo !='android'  AND ROOT_EXTENDS LIKE 'CHECKED%' AND EXCEPTION_EXTENDS LIKE 'RUNTIME'

%SELECT COUNT(*) FROM STACKTRACESUMMARY WHERE
%repo !='android'  AND ROOT_EXTENDS LIKE 'CHEC%' AND EXCEPTION_EXTENDS LIKE 'RUN%';

%SELECT COUNT(*) FROM STACKTRACESUMMARY WHERE
%repo !='android'  AND ROOT_EXTENDS LIKE 'CHEC%' AND EXCEPTION_EXTENDS LIKE 'RUN%'
%and SIGNALER_FROM LIKE 'LIB%';

\begin{table*}
  \centering
  \begin{tabular}{llcccccc}
    \hline
    \bfseries{Wrapper Type}  &  \bfseries{Root Cause Type} &  \bfseries{Projects}  &  \bfseries{Occurrences} & \textsf{Android} & \textsf{Java/Libcore} & \textsf{Lib} & \textsf{App}  \\
    \hline
      %Runtime &  Checked   & 70  / 18 & 114 /  34 &  66 /  9  &  0 /  & 19 / 19 &  29 / 6 \\

      Runtime &  Checked   & 88 & 148 &  75  &  0   & 38 &  35 \\

      %Runtime   &  Error   & 38  \ 8  & 57    &  50 \ 8  &  0   & 6 \ 2  &  1   /  0\\
      Runtime   &  Error   & 46  &  67    &  58  &  0   & 8  &  1   \\

%      Checked &  Runtime   & 12 \ 5  & 22 \ 9 & 4 &  0  & 9 \7 &  9 \ 2 \\
      Checked &  Runtime   & 17  & 31 & 4 &  0  & 16 &  11 \\

%      Checked & Error      & 7 \ 1 &  8 & 5  &  0  & 0 \ 1 &  3 \0 \\

      Checked & Error      & 8 &  9  & 5  &  0  &  1 &  3  \\

 %     Error & Checked      & 4 \ 10  &  7 & 0  \ 6  &  7  & 0 \6 &  0   \ 8    \\
     Error & Checked      & 14 &  27 &  6  &  7  &  6 &   8    \\

%      Error & Runtime     & 6 \ 2  &  13   & 1 &  1  & 0 \ 1 &  11 \ 3    \\

      Error & Runtime     & 8  &  17   & 1 &  1  & 1 &  14    \\

  \hline
      %none   & Runtime   &  2360 & 359 \\
      %none  &   Checked  & 422  & 117 \\
      %none  &   Error   & 381  & 141 \\
      %none &  Undefined  &  15   & 10  \\
      %none & Throwable  &  1    & 1 \\
     %\hline
      %Runtime   & Runtime & 560  & 182 \\    
      %Checked   & Checked & 98   & 42  \\
      %Error     & Error   & 15   & 14  \\
    %\hline
  \end{tabular}
\caption{Wrappings comprising different exception types.}
\label{tab:wrappingandroid}
\end{table*}
